Collective excitations in the 2- and 3-dimensional extended Hubbard model

### 2023-11-29 paper/main.tex
please dont die

\begin{subequations}
    \label{eqn:resolvent_bases}
    \begin{align}
        A_\text{Higgs} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} + f_{vk}^\dagger \right)\,,\\
        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{vk}^\dagger \right)\,,\\
        A_\text{CDW} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right)\,,\\
        A_\text{AFM} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right)\,,
    \end{align}
\end{subequations}

@@

Similar to the previous section, we will first show the general form of the spectral functions with respect to the operators \eqref{eqn:resolvent_bases}.
They are depicted in \autoref{fig:resolvent_overview_AFM}, choosing $V=1$ for the square lattice and $V=0.5$ for the simple cubic lattice.
For the CDW phase (panel a) we chose $V=4.1$ and for the AFM phase (panel b) $V=3.9$.

>>>>

\begin{subequations}
    \label{eqn:resolvent_bases}
    \begin{align}
        A_\text{Higgs} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} + f_{\vk}^\dagger \right)\,,\\
        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right)\,,\\
        A_\text{CDW} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right)\,,\\
        A_\text{AFM} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right)\,,
    \end{align}
\end{subequations}

@@

Similar to the previous section, we will first show the general form of the spectral functions with respect to the operators \eqref{eqn:resolvent_bases}.
They are depicted in \autoref{fig:resolvent_overview_AFM}, choosing $V=1$ for the square lattice and $V=0.75$ for the simple cubic lattice.
For the CDW phase (panel a) we chose $U=ZV + 0.1$ and for the AFM phase (panel b) $V=ZV - 0.1$.
